On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions

### 2013-10-10 paper2.tex
last

%MNRAS
\title[On the Physics of Radio Halos in Galaxy Clusters]{On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions}
\author[F. Zandanel, C. Pfrommer and F. Prada]{
Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,2}$\\
$^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
$^{2}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany, christoph.pfrommer@h-its.org\\
$^{4}$Campus of International Excellence UAM+CSIC, Cantoblanco, E-28049 Madrid, Spain\\
$^{5}$Instituto de F\'{\i}sica Te\'orica, (UAM/CSIC), Universidad Aut\'onoma de Madrid, Cantoblanco, E-28049 Madrid, Spain}
\begin{document}

@@

For the purpose of this section, we adopt the measured gas and temperature
profiles derived from X-ray observations of each cluster.  Our extended model
includes an overall normalization $g_{\rmn{CR}}$ of the CR distribution function
and the hadronically-induced non-thermal emission (Appendix~\ref{app:A}). Note
that this parameter can be interpreted as a functional that depends on the
\emph{maximum CR acceleration efficiency}, $g(\zeta_{\rmn{p,max}})$, but
\emph{only} for $\gamma_{\rmn{tu}}\gtrsim100$ \citep{2010MNRAS.409..449P}. We
will additionally study the CR-to-thermal pressure $X_{\rmn{CR}}=
P_{\rmn{CR}}/P_{\rmn{th}}$, where the CR pressure is given by
\begin{equation}
  \label{eq:PCR}
  P_{\rmn{CR}}=\frac{g_{\rmn{CR}} C m_{\rmn{p}} c^{2}}{6}
  \sum_{i=1}^{3} \Delta_{i} \mathcal{B}_{1/(1+q^2)} \left(
    \frac{\alpha_{i}-1}{2},\frac{3-\alpha_{i}}{2} \right).
\end{equation}
Here, $c$ is the speed of light, $\mathcal{B}_x(a,b)$ denotes the incomplete beta
function, $q=0.8$ is the low-momentum cutoff of the CR distribution, and the
normalization factors of the individual CR populations are given by $\Delta_{i}
= (0.767, 0.143, 0.0975)$ \citep[][see also
Appendix~\ref{app:A}]{2010MNRAS.409..449P}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
We thank Anders Pinzke for many useful discussions and Lawrence Rudnick and Shea
Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful
discussions. We thank Matteo Murgia for kindly providing the radio surface
brightness profiles of Ophiuchucs and Abell~2163 that have been recomputed with
respect to the Reiprich \& B\"{o}ringher (2002) cluster positions, and Wolfgang
Reich for providing the 1.4~GHz radio map of Coma.  We also thank Miguel-Angel
Perez Torres and Huub R{\"o}ttgering for the useful discussions.  Finally, we
thank the MultiDark database people, in particular Adrian Partl and Kristin
Riebe.  F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of
the program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE.
F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's
Consolider-Ingenio 2010 Programme under grant MultiDark CSD2009-00064. C.P.{\
}gratefully acknowledges financial support of the Klaus Tschira Foundation. The
MultiDark Database used in this paper and the web application providing online
access to it were constructed as part of the activities of the German
Astrophysical Virtual Observatory as result of a collaboration between the
Leibniz-Institute for Astrophysics Potsdam (AIP) and the Spanish MultiDark
Consolider Project CSD2009-00064. The Bolshoi and MultiDark simulations were run
on the NASA's Pleiades supercomputer at the NASA Ames Research Center.

>>>>

%MNRAS
\title[On the Physics of Radio Halos in Galaxy Clusters]{On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions}
\author[F. Zandanel, C. Pfrommer and F. Prada]{
Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
$^{1}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
$^{2}$Now at GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany, christoph.pfrommer@h-its.org\\
$^{4}$Campus of International Excellence UAM+CSIC, Cantoblanco, E-28049 Madrid, Spain\\
$^{5}$Instituto de F\'{\i}sica Te\'orica, (UAM/CSIC), Universidad Aut\'onoma de Madrid, Cantoblanco, E-28049 Madrid, Spain}
\begin{document}

@@

For the purpose of this section, we adopt the measured gas and temperature
profiles derived from X-ray observations of each cluster.  Our extended model
includes an overall normalization $g_{\rmn{CR}}$ of the CR distribution function
and the hadronically-induced non-thermal emission (Appendix~\ref{app:A}). Note
that this parameter can be interpreted as a functional that depends on the
\emph{maximum CR acceleration efficiency}, $g(\zeta_{\rmn{p,max}})$, but
\emph{only} for $\gamma_{\rmn{tu}}\gtrsim100$ \citep{2010MNRAS.409..449P}. We
will additionally study the CR-to-thermal pressure $X_{\rmn{CR}}=
P_{\rmn{CR}}/P_{\rmn{th}}$, where the CR pressure is given by
\begin{equation}
  \label{eq:PCR}
  P_{\rmn{CR}}=\frac{g_{\rmn{CR}} C m_{\rmn{p}} c^{2}}{6}
  \sum_{i=1}^{3} \Delta_{i} \mathcal{B}_{1/(1+q^2)} \left(
    \frac{\alpha_{i}-2}{2},\frac{3-\alpha_{i}}{2} \right).
\end{equation}
Here, $c$ is the speed of light, $\mathcal{B}_x(a,b)$ denotes the incomplete beta
function, $q=0.8$ is the low-momentum cutoff of the CR distribution, and the
normalization factors of the individual CR populations are given by $\Delta_{i}
= (0.767, 0.143, 0.0975)$ \citep[][see also
Appendix~\ref{app:A}]{2010MNRAS.409..449P}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
We thank Anders Pinzke for many useful discussions and Lawrence Rudnick and Shea
Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful
discussions. We thank Matteo Murgia for kindly providing the radio surface
brightness profiles of Ophiuchucs and Abell~2163 that have been recomputed with
respect to the Reiprich \& B\"{o}ringher (2002) cluster positions, and Wolfgang
Reich for providing the 1.4~GHz radio map of Coma.  We also thank Miguel-Angel
Perez Torres and Huub R{\"o}ttgering for the useful discussions.  Finally, we
thank the MultiDark database people, in particular Adrian Partl and Kristin
Riebe.  F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of
the program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE.
F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's
Consolider-Ingenio 2010 Programme under grant MultiDark CSD2009-00064, AYA10-21231. 
C.P.{\ }gratefully acknowledges financial support of the Klaus Tschira Foundation. The
MultiDark Database used in this paper and the web application providing online
access to it were constructed as part of the activities of the German
Astrophysical Virtual Observatory as result of a collaboration between the
Leibniz-Institute for Astrophysics Potsdam (AIP) and the Spanish MultiDark
Consolider Project CSD2009-00064, AYA10-21231. The Bolshoi and MultiDark simulations 
were run on the NASA's Pleiades supercomputer at the NASA Ames Research Center.
